---
title: "PSY 8712 Week 8 Project"
author: "Ben Elliott"
date: "`r Sys.Date()`"
output: html_document
output_dir: ../out
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reproducible Image and Online Resources
An image of this project as of *`r Sys.Date()`* can be accessed by [clicking this link](mybinder.org).  
An interactive web app is available by [clicking this link instead](link to the shiny app you create in Part 3).  

# Script Settings and Resources
```{r script settings and resources, results = "hide", echo = TRUE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) # set wd
library(tidyverse) # load libraries
```

# Data Import and Cleaning
Add a short plaintext explaination here (1-2 sentences). I reverse coded based on a judgment that the q items are in Likert-style values of 1 - 5 which allowed me to mutate the variable by subtracting the item value from 6. 
```{r data import and cleaning}
week8_tbl <- read_csv("../data/week3.csv") %>% 
  mutate(
    timeStart = ymd_hms(timeStart),
    condition = factor(condition, levels = c("A", "B", "C"), labels = c("Block A", "Block B", "Control")), 
    gender = factor(gender, levels = c("M", "F"), labels = c("Male", "Female")),
    q5 = 6 - q5
  )
```
# Visualization
