---
title: "PSY 8712 Week 8 Project"
author: "Ben Elliott"
date: "`r Sys.Date()`"
output: html_document
output_dir: ../out
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reproducible Image and Online Resources
An image of this project as of *`r Sys.Date()`* can be accessed by [clicking this link](mybinder.org).  
An interactive web app is available by [clicking this link instead](link to the shiny app you create in Part 3).  

# Script Settings and Resources
```{r script settings and resources, results = "hide", echo = TRUE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) # set wd
library(tidyverse) # load libraries
library(GGally)
```

# Data Import and Cleaning
Add a short plaintext explaination here (1-2 sentences). I reverse coded based on a judgment that the q items are in Likert-style values of 1 - 5 which allowed me to mutate the variable by subtracting the item value from 6. 
```{r data import and cleaning}
week8_tbl <- read_csv("../data/week3.csv") %>% 
  mutate(
    timeStart = ymd_hms(timeStart),
    condition = factor(condition, levels = c("A", "B", "C"), labels = c("Block A", "Block B", "Control")), 
    gender = factor(gender, levels = c("M", "F"), labels = c("Male", "Female")),
    q5 = 6 - q5
  )
```
# Visualization
```{r visualization, echo=FALSE, message=FALSE, warning=FALSE}
glimpse(week8_tbl$q1)

week8_tbl %>%  
  mutate(
    x_mean = rowMeans(across(q1:q6), na.rm = TRUE),
    y_mean = rowMeans(across(q8:q10), na.rm = TRUE)
  ) %>% 
  ggplot(aes(x = x_mean, y = y_mean)) +
  geom_point(position = "jitter", width = .3) +
  geom_smooth(method = "lm", se = TRUE, color = "purple")

```

# Analysis
```{r analysis}
cor_test <- week8_tbl  %>%
  mutate(
    x_mean = rowMeans(across(q1:q6), na.rm = TRUE), 
    y_mean = rowMeans(across(q8:q10), na.rm = TRUE)
  ) %>% 
  {
    cor.test(.$x_mean, .$y_mean)
  }
```

I observed a correlation of `r round(cor_test$estimate, 2)`. Yet the p-value of the correlation test is `r round(cor_test$p.value, 2)` which is non-significant, meaning that we fail to reject the null hypothesis that the mean correlation is zero. 


# Data Export
```{r data export}
(skinny_data <- week8_tbl %>%
  mutate(
    x_mean = rowMeans(across(q1:q6), na.rm = TRUE), 
    y_mean = rowMeans(across(q8:q10), na.rm = TRUE)  
  ) %>% 
  select(timeStart, gender, x_mean, y_mean)) %>% 
  saveRDS(file = "../shiny/shiny_week8/skinny_data.rds")

# Save for later
# library(rsconnect)
#     rsconnect::deployApp('path/to/your/app')
```

